Combining checkpointing and data compression\\ for high frequency seismic imaging

### 2018-10-03 paper/paper.tex
revised Introduction

Compared to using only checkpointing without compression, our combined method
can often achieve better performance. This is achieved by reducing the size of
stored program states, thereby allowing more program states to be stored during
the forward computation. This in turn reduces the amount of recomputations that
needs to be performed during the adjoint computation. On the other hand, the
compression and decompression itself takes time.  We thereforen provide a
comprehensive performance model that predicts whether or not the combined method
is beneficial. We present various scenarios that use a TODO describe Richter and
TODO describe JLSE/SKX node system, error tolerances for the lossy ZFP
compression algorithm ranging from TODO to TODO, and different types of forward
and adjoint computations that vary in their ratio between compute cost and state
size.

>>>>

Compared to using only checkpointing without compression, our combined method
often improves performance. This is a consequence of the reduced size of stored
program states, allowing more program states to be stored during the forward
computation. This in turn reduces the amount of recomputation that needs to be
performed. On the other hand, the compression and decompression itself takes
time. We thereforen provide a comprehensive performance model that predicts
whether the combined method is beneficial, that is, whether the time spent
compressing and decompressing is less than the time saved by reduced
recomputations. We present various scenarios that use a TODO describe Richter
and TODO describe JLSE/SKX node system, error tolerances for the lossy ZFP
compression algorithm ranging from TODO to TODO, and different types of forward
and adjoint computations that vary in their ratio between compute cost and state
size.
